\mytitile\\~

### 2019-11-21 document.tex
Massive updates, pictures recolouring

\begin{figure}
	\includegraphics[width=\linewidth]{experiment}
	\caption{\textbf{(a)} Optical photograph of the device (false coloured). Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator. From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green). \textbf{(b)} The equivalent electrical circuit. Tunable Josephson junctions are in fact SQUIDs with magnetic flux control. \textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly). In this work, we concentrate on the area inside the dashed rectangle.}
	\label{fig:experiment}
\end{figure}

@@

To induce state transitions in a transmon one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line. The interaction term between the transmon and the field is then modelled by the following operator: 
\begin{equation}
\hat H_{dr} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
\end{equation}
where $\Omega$ stands for the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
\end{equation}
where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
After the transformation and application of the RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

	\centering
	\includegraphics[width=\linewidth]{main_picture}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and thus the picture is symmetric. Panel \textbf{(a)} contains an additional horizontal line which origins from a parasitic resonance interacting with the readout resonator but not with the SAM. Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; some other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). In panel \textbf{(b)}, we also denote where possible some of the transitions $\ket{00}\rightarrow \ket{ij/n}$ where $i,j$ stand for the transmon eigenstates and $/n$ is optional for an $n$-photon process.}
	\label{fig:two-tone}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=\linewidth]{stationary}
	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Left picture is same as the right one but with transitions from the stationary Hamiltonian overlaid. The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:statinary_levels}
\end{figure*}

@@

\begin{figure*}
	\includegraphics[width=.49\linewidth]{powerscan}
	\includegraphics[width=.49\linewidth]{zoom2_picture}
	\caption{Investigation of the power dependence of feature II. Dashed are the model curves turning to dotted when the model is no longer expected to be valid (see Section \ref{sec:theory}). Model values for $\Omega_2$ are the same for both panels and shown as annotations in (b). \textbf{(a)} Experiment (second cooldown; the parameters are different from \autoref{fig:experiment}). The power of the microwave source is increased from -20 to 0 dBm so that the amplitude grows linearly, and the proportional growth of the splitting is observed. \textbf{(b)} Simulation with an equal and increasing amplitudes of the driving $\Omega_{1,2}/2\pi=$4.5, 11.25, 22.5 and 45 MHz; other parameters as in \autoref{fig:two-tone}. Note that now colours show the population of the ground state ($\ket{00}$). The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.}
	\label{fig:zoom}
\end{figure*}

@@

\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:statinary_levels}). In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $\ket{ij/n}$ where $i,j$ denote the final transmon states after the transition from $\ket{00}$, and $/n$ is optional for an $n$-photon process. We put the labels at the line of symmetry where the transmons are in their sweet spots; the SAM states at this point are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.

Due to the strong driving, we observe several multiphoton transitions besides the main lines at $\omega_{(1,2)}(\Phi_e)/2\pi$. The $\ket{02/2}$ and $\ket{20/2}$ are very common for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$. Another two-photon process appears as $\ket{11/2}$ line when two qubits are excited simultaneously. This process is used, for example, for doing the bSWAP gate\cite{poletto2012entanglement}; in our case, it is taking part in formation of feature I. A three-photon process $\ket{00}\rightarrow\ket{12/3}$ is also clearly visible just below the $\ket{02/2}$ line. As we will see, it is involved in forming features II and III. Notably, transitions $\ket{11/2}$ and $\ket{12/3}$ are forbidden when there is no interaction ($J=0$). Therefore, it is expected that all Roman-numbered features should only appear with non-vanishing $\hat H_{int}$.

When two lines intersect, they may form an avoided crossing if the corresponding matrix element of $\hat H_{int}$ is non-zero. In such cases, the SAM becomes inseparable with some of the eigenstates becoming superpositions of the factorized states. For a two-transmon SAM, such points are, for instance, crossings between $\ket{01}$, $\ket{10}$ or $ \ket{11} $, $ \ket{02} $($ \ket{20} $). Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between $\ket{12},\ \ket{21}$ at the same $\Phi_e$ where $\ket{01}$, $\ket{10}$ intersect.

\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2. Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).

From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$. The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates $\ket{10}$, but is not visible in \autoref{fig:two-tone}. From additional measurements and simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}~(a),(b). As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz. To fully quantify the size of the splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines

We come to the same conclusion for feature I: increasing drive amplitude on one of the transmons while keeping the other one small and constant again elicits an avoided crossing with a proportionally enlarging splitting (see \autoref{fig:difdrive}). Notably, two qualitatively different patterns of avoided crossings arise when the first or the second qubit is strongly driven.

These observation lead to understanding that the effect is caused by light dressing. In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time. We will discuss these effects in greater detail in \autoref{sec:theory}.

\begin{figure*}
	\centering
	\includegraphics[width=.9\linewidth]{main_scheme}
	\caption{Explaining the origin of the AT satellites for feature III. \textbf{(a)} System level structure at 3.65 mA. At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$. The first transmon is driven by a strong signal of amplitude $\Omega_1$ at a small detuning $\Delta_1$ from $\omega_1$ shown in green. The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles. \textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$). However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = (\Omega_1^2 + \Delta_1^2)^{\frac{1}{2}}$ (the first transmon becomes light-dressed). \textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{dr}^2$ are shown with blue ellipses). In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$. In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure*}

\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1-5 as well. Feature2 is a small avoided crossing between $\ket{02/2}$ and $\ket{21/3}$. It is missing in the stationary solution and thus is a manifestation of dressing by light. Feature 2 is its twin: $\ket{12/3}$ and $\ket{20/2}$ intersect but the avoided crossing is smaller and is not resolved due to the asymmetry of the driving strengths. Feature 3 is a large avoided crossing between $\ket{12/3}$ and $\ket{21/3}$ predicted by the model. A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator. Feature 4 is explained by the stationary model and is a consequence of multiple spectral lines of a peculiar shape formed by a pair of avoided crossings passing through a single point (dotted lines in \autoref{fig:statinary_levels}). It appears at the point where $\ket{02/2}$ intersects $\ket{20/2}$ and is just barely visible in the experimental data due to the noise. Feature 5 is located at the intersection between $\ket{20/2}$ and normally invisible $\ket{10}\rightarrow \ket{02}$, and can be found in the experimental data, too.

Finally, when the coupling is turned off ($J=0$) in modelling, the system does not demonstrate any of the described details. This means that all these effects can only be attributed to the SAM as a whole.

@@

Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to cause them. For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}. However, in our case the level structure is more complicated.

First of all, since during the spectroscopy we apply only a single microwave tone ($\omega_d^1 = \omega_d^2$), for the A-T effect it has to be simultaneously the coupler and the probe; the latter must be much weaker than the former, as well. These conditions are satisfied when $\omega_{(2,1)} = \omega_{(1,2)}+\alpha_{(1,2)}/2$  where we can simultaneously excite transitions $01 (10)$ and $20/2 (02/2)$ (features II and III, respectively) because the of the two-photon probe. Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure. In contrast, the single-photon excitation is enough to dress the system. In other words, in our case the A-T coupling operator is $\hat H_{dr}^1$ (strong), and the probing operator is $\hat H_{dr}^2$ (weak in the two-photon regime). Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.

Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$. However, as we will show, for the avoided crossing of feature I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$. Below, we give the detailed explanation concerning features II and III, and finally, I.

@@

In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect would occur for feature III. For simplicity, we  \autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM. Since from numerical simulations we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line, and hereinafter we consider the first transmon as a two-level system.

The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}. Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$. At the same time, the second transmon energies stay the same.

Finally, in \autoref{fig:main_scheme}~(c) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{dr}^2$. In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$. The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states. From here it becomes obvious that without the transmon-transmon interaction the sideband transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.  Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.

Now, we will repeat this reasoning using a quantitative mathematical model. We start from the initial Hamiltonian \eqref{Hsystem}. To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
\begin{equation}
R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
\end{equation}  
Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$:
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{dr}^2 - \omega_{dr}^1$.

>>>>

\begin{figure}
	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical photograph of the device (false coloured). Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator. From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green). \textbf{(b)} The equivalent electrical circuit. Tunable Josephson junctions are in fact SQUIDs with magnetic flux control. \textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly). In this work, we concentrate on the area inside the dashed rectangle.}
	\label{fig:experiment}
\end{figure}

@@

To induce state transitions in a transmon one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line. The interaction term between the transmon and the field is then modelled by the following operator: 
\begin{equation}
\hat H_{d} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
\end{equation}
where $\Omega$ stands for the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.

Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
\begin{align}
&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
\end{align}
After the transformation and application of the RWA:
\begin{equation}
\begin{aligned}
	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
	\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
\end{aligned}
\label{eq:RWA}
\end{equation}

@@

	\centering
	\includegraphics[width=\linewidth]{main_picture}
	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}. Colour shows the real part of complex transmission  through the sample. Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture. Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator. Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description). We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process.}
	\label{fig:two-tone}
\end{figure*}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{stationary}
	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour). Lines show various transition frequencies from the stationary Hamiltonian. The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
	\label{fig:statinary_levels}
\end{figure}

@@

\begin{figure*}
	\includegraphics[width=.49\linewidth]{powerscan}
	\includegraphics[width=.49\linewidth]{zoom2_picture}
	\caption{Power dependence of feature II: experiment and theory. Dashed are the model curves turning to dotted when the model is not expected to be valid (see Sections \ref{sec:theory} and \ref{sec:münchhausen}); model values for $\Omega_2$ are the same for both (a) and (b): $\Omega_{2}/2\pi=$ 4.5, 11.25, 22.5 and 45 MHz. \textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}). The power of the microwave source is increased from -20 to 0 dBm and the corresponding growth of the splitting and the widths of the spectral lines is observed. \textbf{(b)} Simulation with amplitudes of the driving $\Omega_{1,2}$ equal to the model values; other parameters as in \autoref{fig:two-tone}. Note that now colours show the population of the ground state.}
	\label{fig:zoom}
\end{figure*}

\begin{figure}
	\includegraphics[width=\linewidth]{powerscan_1d}
	\caption{Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV. From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
	\label{fig:splitting_linear}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{topological_splittings}
	\caption{Simulated population of the ground state when the transmons are driven at different amplitudes $\Omega_{1,2}$ but at the same frequency. In the left (right), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger. Gray dashed lines show the stationary solution, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
	\label{fig:difdrive}
\end{figure}

@@

\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:statinary_levels}). In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon states after the transition from the ground state, and $/n$ is optional for an $n$-photon process. We put the labels at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.

Due to the strong driving, we observe several multiphoton transitions besides the main lines at $\omega_{(1,2)}(\Phi_e)/2\pi$. The ${02/2}$ and ${20/2}$ are very common for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$. Another two-photon process appears as $11/2$ line when two qubits are excited simultaneously. This process is used, for example, for doing the bSWAP gate\cite{poletto2012entanglement}; in our case, it is taking part in formation of feature I. A three-photon process $12/3$ is also clearly visible just below the $02/2$ line. As we will see, it is involved in forming features II and III. Notably, transitions $11/2$ and ${12/3}$ are forbidden when there is no interaction ($J=0$). Therefore, it is expected that all Roman-numbered features should only appear with non-vanishing $\hat H_{int}$.

When two lines intersect, they may form an avoided crossing if the corresponding matrix element of $\hat H_{int}$ is non-zero. In such cases, the SAM becomes inseparable with some of the eigenstates becoming superpositions of the factorized states. For a two-transmon SAM, such points are, for instance, crossings between ${01}$, ${10}$ or $ {11} $, $ {02} $($ {20} $). Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between ${12}/3,\ {21}/3$ at the same $\Phi_e$ where ${01}$, ${10}$ intersect.

\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2. Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition ${01}$ intersects with the two-photon one ${20/2}$ (${10}$ intersects ${02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).

From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$. The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}. In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$. From additional measurements and simulations, we have found that the size of these anticrossings depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b). As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the ${01}$ spectral line which is approximately $\Omega_2/2\pi$ Hz. To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}. By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:splitting_linear}).

We see a similar behaviour for feature I: increasing drive amplitude on one of the transmons while keeping the other one small and constant again elicits avoided crossings with the proportional size. In \autoref{fig:difdrive} we show only the simulation results; an experiment is not possible with our sample because there is no way to adjust the driving amplitudes $\Omega_{1,2}$ individually. We note that two qualitatively different patterns arise depending on which of the transmons is driven stronger than the other. From this and from the shape of the splitting in feature I of \autoref{fig:experiment}~(a), we can infer that $\Omega_1 \approx 2\Omega_2$ there.

These observations mean that I -- III are caused by light dressing. In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time. We will discuss these effects in greater detail in \autoref{sec:theory}.

\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1 -- 5 as well.

Feature 1 is a small avoided crossing between ${02/2}$ and ${21/3}$. It is missing in the stationary solution and thus is caused by the light dressing just as I -- III. Feature 2 is its twin: ${12/3}$ and ${20/2}$ intersect there but the anticrossing is smaller due to the asymmetry of the driving strengths and is not resolved.

Feature 3 is a large avoided crossing between three-photon processes ${12/3}$ and ${21/3}$. It is predicted by the stationary model, and direct diagonalization yields the splitting of $\frac{4}{3}J$. A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator in the third order.

Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:statinary_levels}). It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise. Feature 5 is located at the intersection between ${20/2}$ and normally invisible ${10} - {02}$, and can be found in the experimental data, too.

Finally, when the coupling is turned off ($J=0$) in the simulation, the system does not demonstrate any of the described details. This means that all these effects can only be attributed to the SAM as a whole.

@@

Since we had already connected the additional avoided crossings with the light dressing, it was natural to expect the Autler-Townes effect to be at the root of the avoided crossings. For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}. However, in our case the level structure and the effect itself are more complicated.

First of all, since during the spectroscopy we apply only a single microwave tone ($\omega_d^1 = \omega_d^2$), for the A-T effect it has to be simultaneously the coupler and the probe; the latter must be much weaker than the former, as well. These conditions are satisfied when $\omega_{(2,1)} = \omega_{(1,2)}+\alpha_{(1,2)}/2$  where we can simultaneously excite transitions $01 (10)$ and $20/2 (02/2)$ (features II and III, respectively) because the of the two-photon probe. Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure. In contrast, the single-photon excitation is enough to dress the system. In other words, in our case the A-T coupling operator is $\hat H_{d}^1$ (strong), and the probing operator is $\hat H_{d}^2$ (weak in the two-photon regime). Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.

Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$. However, as we have demonstrated in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.

Below, we give the detailed explanation of features II and III, and finally, I.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} Schematic of the transition frequencies near III (not to scale). Red dashed line shows the current (0.36 mA) where the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$ and several transitions become resonant. So far we assume that each transmon is driven at its own frequency. \textbf{(b)} System level structure at the resonant point including the driving $\hat H_{d}^1$ of the first transmon by a strong signal of amplitude $\Omega_1$ (orange ellipses) at a small detuning $\Delta_1$ from $\omega_1$. The second transmon driving is not shown here. Action of $\hat H_{int}$ in RWA is depicted as orange-blue circles. \textbf{(c)} In the frame rotating with the drive of the first transmon, all the states $\ket{0j},\ket{1j}$ become nearly degenerate ($\omega_1 \rightarrow \Delta_1$). Dressing by the strong excitation increases this splitting to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$. \textbf{(d)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{d}^2$ are shown with blue ellipses). In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$. In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

\begin{figure}
	\includegraphics[width=.9\linewidth]{topo_scheme}
	\caption{Explaining feature I. (a) Schematic of the transitions near I. (b) Transitions in the frame rotating with the second transmon with dressing. As will be shown in Section \ref{sec:münchhausen}, in our experiment there can only be one visible transition to the left or to the right from the resonance.}
	\label{fig:featureI}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III. For simplicity, we will temporarily assume that each transmon is driven at its own frequency (this assumption will be lifted in the following section). For convenience, in \autoref{fig:main_scheme}~(a) we schematically reproduce the transitions near III where the first transmon (orange) is below the second (blue), and the resonance point in current is shown with dashed red line. Next, \autoref{fig:main_scheme}~(b) demonstrates the stationary level structure of the SAM at 0.36 mA. Nearly-resonant with $10$ (detuning $\Delta_1$) single-photon driving with $\hat H_d^1$ is shown with orange ellipses while much weaker two-photon $\hat H_d^2$ is not shown yet. Since from numerical simulations we know that the third level of the first transmon is not necessary to observe the splitting, $\ket{02}$ is shown transparent, and hereinafter the states $\ket{j2},\ j=0..2$ are not used in the modelling.

The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(c)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}. Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$. Meanwhile, the second transmon energies stay the same.

Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{d}^2$. In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$. The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states. From here it becomes obvious that without the transmon-transmon interaction the sideband transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.  Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.

Now, we will repeat this reasoning using a quantitative mathematical model. We start from the initial Hamiltonian \eqref{Hsystem}. To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
\begin{equation}
R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
\end{equation}  
Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$:
\begin{equation}
\begin{aligned}
\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
\hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
\end{aligned}
\end{equation}
where $\delta = \omega_{d}^2 - \omega_{d}^1$.
